\startproduct out_of_the_blue
\usepath[{..}]
\environment screenplay

\startfrontmatter
\startcoverpage
\title{Out of the Blue}
\subtitle{An Excerpt of a Screenplay}
\author{Daniel Joseph Pezely}
\vfill
\startalignment[flushleft]
Copyright 2004
\stopalignment
\vfillneg
\stopcoverpage
\stopfrontmatter

\definecharacter[bob]
\definecharacter[jainene]
\definecharacter[kathy]
\definecharacter[jenkins][name={Mrs.~Jenkins}]
\definecharacter[nancy]
\definecharacter[emma]
\definecharacter[william]
\definecharacter[dave][name={Big Dave}]

\startbodymatter

\interior[night]{Sport-utility truck}

\bob and \jainene are a thirty-something couple. He's driving a trendy
sport-utility truck with her in the passenger seat with her eyes close,
relaxed, drifting close to sleep. Snow is caked on the windshield where the
wipers are unable to reach.

A loud bang followed by severe shaking, their truck crashes. She doesn't even
have time to scream.

\cut

\interior[night]{hallway}{hospital}

\kathy, a nurse approximately the same age as \jainene pushes her down a long
hallway in a wheel chair. \jainene has a neck-brace, a black eye, an arm in a
sling, and her blouse is torn revealing a very plain bra strap.

\startkathy
Your fianc\'e needs you to be strong\.

You may doubt that he can hear you, but tell him that you love him. Tell him
how much he means to you\.

It'll be hard, but coming to visit even if he's in a coma should help him.
Especially then\.

While doctors won't comment on that officially... They don't want to give
people "false hope," blah, blah, blah,... But in twelve years as a nurse, I've
seen a lot\.

If you can believe in miracles...
\stopkathy

\startjainene
I don't believe in anything right now.
\stopjainene

\interior[continuous]{emergency room lobby}{hospital}

The nurse wheels \jainene into the lobby. \bob's mother, \jenkins comes to
\jainene.

\startjainene
How is he? Have you seen him?
\stopjainene

\startjenkins
They said he is stable now, but he's still unconscious. We just came down from
his room\.

They're running more tests now.
\stopjenkins

\startjainene
Why is this...?
\stopjainene

A brief pause.

\startjainene[continued]
What's going to happen?
\stopjainene

\startjenkins
Shhh. Everything's going to be okay. Everything's going to be okay...
\stopjenkins

\kathy touces \jenkins' forearm.

\startkathy
Excuse me... \jenkins?
\stopkathy

\startjenkins
Yes?
\stopjenkins

\startkathy
You're talking about your son?
\stopkathy

\startjenkins
Yes.
\stopjenkins

\startkathy
He's here in the--? He's your--?

\(to \jainene)

He's your--? He was the driver! Oh... my... god!
\stopkathy

\jainene and \jenkins just look at nurse \kathy.

\startkathy[continued]
\(to \jenkins)
It's me... \kathy. I went to high school with him... Remember?
\stopkathy

No reply from \jenkins.

\startkathy[continued]
Umm, I look pretty different --
\stopkathy

Interrupting herself and realizing what the mother really needs right now,
\kathy places her hand on \jenkins' arm in a reassuring manner.

\startkathy
I'm sorry. I didn't mean to interrupt. Look, I know the doctors up there\.

He's in the best hands\.

He really is!
\stopkathy

\nancy and \emma arrive, both around \jainene's age and socio-economic bracket.

\startnancy
Oh, you poor thing!
\stopnancy

\startemma
How are you?
\stopemma

\cut

\interior[night]{hallway}{apartment building}

Upon returning home, \jainene and her two friends encounter a neighbor,
\william, who is approximately the same age.

\startsplit

\startnancy
Excuse me.
\stopnancy

\split

\startemma
Pardon us.
\stopemma

\stopsplit

\startwilliam
Geez! What happened?
\stopwilliam

\startnancy
Oh. Hi. \william, isn't it?
\stopnancy

\startwilliam
Yes.
\stopwilliam

\startemma
Car crash.
\stopemma

\jainene fumbles for her keys, then \emma takes over.

\startnancy
The truck is completely totalled.
\stopnancy

\startwilliam
\(to \jainene)

And you?
\stopwilliam

\startjainene
Mostly just bruises.
\stopjainene

\startwilliam
Are you okay otherwise?
\stopwilliam

\jainene is unable to get words out.

\startemma
\bob\ -- her fianc\'e -- is in a coma.
\stopemma

\startwilliam
I'm so sorry!
\stopwilliam

\startjainene
This can't be real.
\stopjainene

\emma and \nancy get \jainene through the door. \william announces his offer
just as the door closes.

\startwilliam
If you need anything, just --
\stopwilliam

\interior[continuous]{\jainene's apartment}{apartment building}

\jainene enters her apartment and walks by her desk. The answering machine has
several messages. Thoroughly perused copies of The New York Times, Wall Street
Journal, The Times of London and others are on the desk. Various books on
business negotiation and legal mediation grace the bookshelves.

\emma and \nancy help \jainene ease herself into a chair.

After the momentary pain of that subsides, she begins to cry.

\cut

\interior[day]{office}

At \jainene's cubicle, a much older distinguished gentleman in a dark flannel
suit, \dave, drags a chair over. She still has one arm in a sling and many
bandages, bruises.

\startdave
I want you to know that we're all looking out for you.
\stopdave

\startjainene
Thanks. That means a lot. Especially, coming from the top.
\stopjainene

\startdave
Right now, I want you to rest and recuperate. We still need you here, but some
of your projects have been handed off. You'll still participate as an advisor.
\stopdave

\jainene starts shaking her head in disappointment.

\startjainene
I've worked so hard on the Columbia project. It's almost complete. You can't
take me off now.
\stopjainene

\startdave
You need your strength, and I need you to be ready for something coming down
the pike.
\stopdave

\startjainene
What?
\stopjainene

\startdave
You'll know soon enough\.

But for now, it's just between you and I.
\stopdave

\startjainene
Until then?
\stopjainene

\startdave
Don't worry.
\stopdave

\startjainene
But I do. You're giving it to Mike Griffin, aren't you?
\stopjainene

\startdave
That's up to your manager. I really don't know.
\stopdave

\jainene lets out a sigh of disbelief.

\cut

\interior[evening]{hallway}{apartment building}

Returning from a day at the office, \jainene is still wearing business attire.
She drops her keys, as it's difficult maneuvering. William hears the noise and
comes out of his apartment.

\startwilliam
How do you feel?
\stopwilliam

\startjainene
Emotionally or physically?
\stopjainene

\startwilliam[tolerance=verystrict]
I know of some things that might help -- that {\underbar will} help\.

Less pain\.

Faster healing\.

There are various healing arts practices from cultures around the world.
\stopwilliam

\jainene is unenthused.

\startwilliam
Trust me. I teach cultural anthropology at the university. I'm very familiar
with these\.

There are classes all over town, and I can recommend a couple of instructors.
\stopwilliam

\jainene is unimpressed.

\startwilliam
It'll save on medical expenses.
\stopwilliam

Now he has her attention.

\interior[continuous]{\jainene's apartment}{apartment building}

The clock reads approximately 6 PM. \jainene enters her apartment and checks
phone messages.

\definecharacter[message]

\startmessage
We're so sorry to hear about the accident. We just heard. Call us when you're
better. Okay...\? Oh, this is Jackie.
\stopmessage

Meanwhile, \jainene attempts stacking and sorting a pile of several unread
newspapers still in their delivery bags, but the pain is too much.

\startmessage[tolerance=verystrict]
Hiya. It's Linda\. We hope you're doing well considering your wedding was
supposed to be in a couple of weeks\. How long will you wait for him?
\stopmessage

\jainene sits, takes off the sling and begins to massage her shoulder.

\startmessage
\bob, the bastard, he had to put himself in a coma to get out of helping his
best friend, didn't he? Sorry, bad joke\. Umm... You have a brother, right? Can
I get his number?
\stopmessage

She peers under the bandage on her shoulder.

\startmessage
Hi! It's Jane! Oh, I heard you're taking the bus to work now since your truck
was totalled. You must be so embarrassed\. I don't think we should cancel --
umm, postpone -- the shower. It'll cheer you up\! Besides, I have such a
fabulous gift, and I can't wait to see your face. Anyway. Call me!
\stopmessage

She heads into the bathroom to get a better look at her wound.

\startmessage
It's me. We can't meet this week\. I know we had planned it for a while, but
something came up\. I'll give you a call when we get back from the Bahamas.

\(pause)

That was your last message.
\stopmessage

\cuttoblack

\credits\leavevmode

\theend

\stopbodymatter

\stopproduct
