\startproduct the_great_adventure
\usepath[{..}]
\environment stageplay

% \setupstage[
%   style=\emph,
%   alternative=text,
%   left=2in,
% ]

\startfrontmatter
\startcoverpage
\title{The Great Adventure}
\subtitle{An Excerpt of a Play}
\author{Arnold Bennett}
\vfill
\startalignment[flushleft]
Copyright 1913
\stopalignment
\vfillneg
\stopcoverpage
\stopfrontmatter

\definecharacter[shawn][fullname={Albert~Shawn}]
\definecharacter[carve][prefix={Mr.~}, fullname={Ilam~Carve}]
\definecharacter[pascoe][prefix={Dr.~}]

\startbodymatter

\act
\scene

\startopen
Front room on ground floor at 126 Redcliffe Gardens. An apartment furnished
richly but in an old-fashioned way. Fine pictures. Large furniture. Sofa near
centre. General air of neglect and dustiness. Carpet half-laid. Trunks and bags
lying about in corners, some opened. Men's wearing apparel exposed.
Mantelpiece, R., in disorder. At back double doors (ajar) leading to another
room. Door, L., leading to hall and front door.
\stopopen

\(\shawn[fullname] is reclining on the sofa, fully dressed, but obviously ill:
an overcoat has been drawn over his legs. A conspicuous object is a magnificent
light purple dressing-gown thrown across a chair. Door bangs off. Enter
\carve[fullname] in his shirt sleeves, hurriedly. \shawn feebly tries to get
up.)

\startcarve
Now, don't move. Remember you're a sick man, and forget you're a servant.
\stopcarve

\(\shawn shivers. \carve, about to put on his dressing-gown, changes his mind,
and wraps it round \shawn as well as he can. \carve then puts on an oldish
coat.)

\startshawn
\(feebly) You've been very quick, sir.
\stopshawn

\startcarve
I found a red lamp only three doors off\. He'll be along in half a minute.
\stopcarve

\startshawn
Did you explain what it was, sir?
\stopshawn

\startcarve
\(genially) How could I explain what it was, you fool, when I don't know\? I
simply asked to see the doctor, and I told him there was a fellow-creature
suffering at No. 126, and would he come at once\. "126?" he said, "126 has been
shut up for years."
\stopcarve

\startshawn
\(trying to smile) What did you say, sir?
\stopshawn

\startcarve
I said \(articulating with clearness) a hundred and twenty-six—and ran off.
Then he yelled out after me that he'd come instantly...\.

I say, \shawn, we're discovered. I could tell that from his sudden change of
tone\. I bet the entire street knows that the celebrated Me has arrived at
last\. I feel like a criminal already, dashed if I don't! I wish we'd gone to a
hotel now.

\(walks about) I say, did you make up the bed?
\stopcarve

\startshawn
I was just doing it, sir.
\stopshawn

\startcarve
But what about the sheets and so on?
\stopcarve

\startshawn
I bought some this morning, ready hemmed, sir - with those and the travelling
rug --
\stopshawn

\startcarve
Well, don't you think you could work your passage out to the bed? With my help?
\stopcarve

\startshawn
Me in your bed, sir!
\stopshawn

\startcarve
\(genially bullying) Keep on in that tone - and I'll give you the sack on the
spot. Now then. Try -- before the doctor comes.
\stopcarve

\(Bell rings.)

\startshawn
The bell, sir - excuse me.
\stopshawn

\startcarve
Confound --
\stopcarve

\(Exit \carve. \shawn coughs and puts a handkerchief to his mouth. \carve
returns immediately with \pascoe[prefix]\pascoe.)

\startpascoe
\(glancing round quickly) This the patient?
\stoppascoe

\(\pascoe goes to \shawn, and looks at him. Then, taking a clinical thermometer
from his pocket and wiping it.)

\startpascoe
\(with marked respect) Allow me to put this under your tongue for half a
minute.
\stoppascoe

\(Having done so, \pascoe takes \shawn's wrist and, looking at his watch,
counts the patient's pulse.)

\startpascoe
\(to \carve, in low curt voiced) When did this begin?
\stoppascoe

\startcarve
Just now. That is, he only began to complain about six o'clock. We arrived in
London this morning from Madrid.
\stopcarve

\startpascoe
\(reading thermometer) Temperature 104-1/2. Pulse is 140 - and weak. I must
have some boiling water.
\stoppascoe

\startcarve
\(at a loss) What for?
\stopcarve

\startpascoe
What for? For a poultice.
\stoppascoe

\startcarve
\(helplessly) But there isn't any...we've nothing except this spirit-lamp.

\(pointing to lamp on table)
\stopcarve

\startpascoe
No women in the house?
\stoppascoe

\startcarve
\(with humour that the doctor declines to see) Not one.
\stopcarve

\startpascoe
\(controlling his exasperation) Never mind. I'll run round to the surgery and
get my hypodermic.

\(to \shawn, reassuringly and deferentially) I shall be back at once,
\carve[prefix]\carve.

\(to \carve, near door) Keep your master well covered up - I suppose you can do
that?
\stoppascoe

\(Exit.)

\startcarve
\shawn, my poor fellow, he takes you for the illustrious \carve[fullname]\.
This is what comes of me rushing out in shirt sleeves.

\(gesture of despair) I can't explain it to him.
\stopcarve

\startshawn
But --
\stopshawn

\startcarve
It's all right. You'll be infinitely better looked after, you know, and I shall
be saved from their infernal curiosity.
\stopcarve

\startshawn
It's only this, sir. I was half-expecting a young a young lady to-night, sir.

\(very feebly) At least, I believe she's young.
\stopshawn

\startcarve
\shawn, I've always suspected you were a bad lot. Now I know. I also know why
you were so devilish anxious to put me to bed early\. What am I to say to this
young lady on your behalf?
\stopcarve

\(\shawn worse, too ill to answer. Pause. Re-enter \pascoe[prefix]\pascoe, very
rapidly, with a large tumbler half-full of hot liquid.)

\startpascoe
You may say I've been quick.

\(as he bends down to \shawn, addressing \carve) Get me a wine glass of clean
cold water.

\(to \shawn) Now, please. I want you to drink a little brandy and water.

\(\shawn makes no response.) By Jove!
\stoppascoe

\(The doctor pours some of the brandy and water down \shawn's throat.)

\startcarve
\(who has been wandering about vaguely) I don't think we've got a wine glass.
There's a cup, but I suppose that isn't medical enough.
\stopcarve

\startpascoe[tolerance=verytolerant]
\(taking a syringe from his pocket and unscrewing it) Pour some water in it.

\(\carve obeys) Now, hold it.
\stoppascoe

\startcarve
\(indicating syringe) What is this device?
\stopcarve

\startpascoe
This device? I'm going to get some strychnine into him by injection\. Steady
with that cup, now!
\stoppascoe

\(\pascoe drops a tablet into the syringe and screws it up again, draws a
little water up into the syringe and shakes the syringe. Then he goes to Shawn
to make the injection, on the top side of the patient's forearm. \carve still
holds the cup out mechanically.)

\startpascoe
I've done with that cup.
\stoppascoe

\startcarve
\(putting the cup down) Might I ask what's the matter with him?
\stopcarve

\startpascoe
Pneumonia is the matter.
\stoppascoe

\(Noise of some one in the hall.)

\startcarve
\(startled) Surely that's some one in the hall.
\stopcarve

\startpascoe
Keep perfectly calm, my man. It's my assistant. I left the door open on purpose
for him. He's got the poultice and things.

\(in a loud voice as he finishes the injection) Come along, come along there.
This way.
\stoppascoe

\theend

\stopbodymatter

\stopproduct
